Anomalous waves triggered by abrupt depth changes: experimental measurements and deterministic-statistical truncated KdV theory

### 2019-10-09 paper2_JNLS/paper.tex
NM

%----------------------------------------------------------%
% Experiments
%----------------------------------------------------------%
\section{The experiments}

@@

	We now aim to compare the statistics measured in the experiments versus the theory. We focus on the representative set of experiments, detailed in Section BLAH and Table BLAH. In these experiments, the peak downstream skewness is precisely 0.83. According to Fig.~\ref{transfig}, we can achieve that value of skewness for the case $(\Lambda, \lamfac) = (16, 8)$ by setting $\thup = 17$, which gives $\thdn = 13.5$. We thus run the DNS with these model parameters (and with a sufficiently fine timestep, and number of samples, and to a final dimensionless time of 10).

\vsp{5}
Figure \ref{uhist} shows histograms of the displacement $u$ from experiments and from TKdV theory. The experimental measurements have been normalized for comparison purposes. The comparison is fucking amazing! Offers convincing evidence that the theory works and the parameters have been matched as well as possible. (At some point, I need to mention the minor point about the forcing spectrum not being matched to the Gibbs measure because it came first).

>>>>

%----------------------------------------------------------%
% Experiments
%----------------------------------------------------------%
\section{The experiments}
\label{experiments}

@@

	We now aim to compare the statistics measured in the experiments versus the theory. We focus on the representative set of experiments, detailed in Section \ref{experiments} and Table \ref{paramtable}. In these experiments, the peak downstream skewness is precisely 0.83. According to Fig.~\ref{transfig}, we can achieve that value of skewness for the case $(\Lambda, \lamfac) = (16, 8)$ by setting $\thup = 17$, which gives $\thdn = 13.5$. We thus run the DNS with these model parameters (and with a sufficiently fine timestep, and number of samples, and to a final dimensionless time of 10).

\vsp{5}

Figure \ref{uhist} shows histograms of the displacement $u$ from experiments and from TKdV theory for comparison. The experiment histograms representative exactly the same data as shown in Fig.~\ref{ExpDiagStats}, only converted to the dimensionless variables. As mentioned previously, the upstream histogram is nearly symmetric, while downstream histogram skews strongly towards positive displacement. The TKdV histograms do a remarkable job of recovering these features, appearing to produce nearly exactly the same distributions, both in shape and in scale.
%
This comparison offers convincing evidence that the theory works and the parameters have been matched as well as possible.
